
\begin{recipe}[250-cookies]{\$250 Cookies}\tag{cookies}
  \rating    4
  \nutrition 4
  \health    1
  \workload{medium}
  \time{120}
  \yield{3 dozen 50\,g cookies}
  \servings{15}
  \source{Internet/custom}
  \maketitle

  \begin{ingredients2}
    4 \oz & chocolate bar (blended)\\
    1\half \cup & nuts (blended)\\
    2\half \cups & oatmeal (blended)\\
    1 \t & baking powder\\
    1 \t & baking soda\\
    \half \t & salt\\
    1 \cup & wheat flour\\
    1 \cup & bread flour\\
    1 \cup & sugar\\
    1 \cup & brown sugar\\
    1 \cup & butter\\
    2 & eggs\\
    1 \t & vanilla\\
    12 \oz & chocolate chips
  \end{ingredients2}

  Blend in batches: chocolate bar; nuts (in 2 batches); oats (in 2
  batches). Dump everything to to the butter into a bowl and mix with your
  hands until butter fully incorporated. Add Eggs and vanilla and mix with
  hands until incorporated. Add chocolate chips and mix with hands. Ball
  out onto a pan, press to flatten slightly, and bake 10--12 minutes at
  \tempF[190]{375}.

  TO TRY: 1~c br sugar, 3/4~c sugar, 1/4~c corn syrup

  \begin{history}
    Original recipie called for double the amount of each ingredient which
    will make a boatload of cookies.

    This recipe made its rounds as an urban legend about a person who was
    tricked into paying Nieman-Marcus \$250 to purchase the recipe. The
    victim wanted everyone to forward the message for revenge. The story
    may be nonsense, but the cookies are good.
  \end{history}
\end{recipe}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../Cookbook"
%%% End:
