
\begin{recipe}{Cinnamon Rolls}%\tag{}
  \rating    3
  \nutrition 2
  \health    2
  \workload{medium}
  \time{180}
  \yield{12}
  \servings{4}
  \source{Dean}
  \maketitle
  % \photo{}

  \section{Rolls}
  \begin{ingredients2}
    1 \cup & milk\\
    1 \T & sugar\\
    1 \T & yeast\\
    \half \cup & sugar\\
    6 \T & butter\\
    1 & egg\\
    1 \t & vanilla\\
    4 \cups & flour\\
    & salt\\
    1 \t & cinnamon
  \end{ingredients2}

  \textsl{Note:} Bring butter and cream cheese for frosting to room
  temperature.

  \textsl{Option:} Try using half milk and half yogurt?

  Warm milk slightly with 1~\T sugar to make yeast happy, proof the yeast.
  Mix sugar, melted butter, egg, and vanilla and combine with yeasty milk.
  Knead in flour, salt, and cinnamon. Let rise until double in size.

  \section{Filling}
  \begin{ingredients2}
    \fourth \lb & \wrap{walnuts or pecans, finely chopped (opt)}\\
    2\half \T & cinnamon\\
    \half \t & nutmeg (opt)\\
    1 \cup & brown sugar\\
    6 \T & butter
  \end{ingredients2}

  Combine brown sugar and cinnamon. When dough ready, roll out to
  $24\times12$ inch rectangle. Brush all the butter over the dough then
  spread the cinnamon and sugar. Roll into a 24 inch log and cut into 2
  inch rolls using a length of floss.

  \section{Sticky topping option}
  \begin{ingredients2}
    4 \T & butter\\
    1 \cup & brown sugar\\
    \half \cup & maple syrup
  \end{ingredients2}
  Heat to disolve sugar. Pour into pan underneath the rolls.

  Place in greased $9\times13$ inch pan. At this point, may place in
  refrigerator to continue the next morning. Let rolls rise to double size.

  \section{Frosting option}
  \begin{ingredients2}
    8 \oz & cream cheese\\
    4 \T & butter\\
    2 \t & vanilla\\
    1\half \cups & powdered sugar
  \end{ingredients2}

  Whip cream cheese, butter, and vanilla. Stir, then whip in powdered
  sugar. Do not refrigerate afterwards.

  Once rolls have risen to the point that they are touching in the pan,
  bake at \tempF[190]{350} for 30 minutes.
\end{recipe}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../Cookbook"
%%% End:
