Steven Brust's Hungarian-style Fra Diavolo Sauce

I call it Hungarian style because of how you cook the onion, which is the
way you prepare onion for a paprikas or a perkholt; everything else is
fairly standard Italian. But it's amazing how much difference it makes if
you do the onion this way.

    1 cube chicken bouillon
    1 Anaheim pepper, diced
    2 jalapeno peppers, diced
    1 can tomato sauce (I use Cantadina cuz I like it)
    2 cans diced tomatoes (you know, the usual can size)
    2 packages fresh mini-bella mushrooms
    2 packages fresh assorted or white mushrooms. (You know, the usual size packages of fresh mushrooms come in)
    2 green peppers, diced
    2 red peppers, diced
    3 lbs spicy Italian sausage (bulk, or chopped if you get links)
    2 really fucking big yellow onions, diced
    1 1/2 heaping soup spoons of fresh minced garlic
    A bunch of oregano (fresh, if possible, dried if necessary)
    Basil
    Cayenne pepper
    Crushed and dried red pepper
    Marjoram
    salt
    black pepper
    1 1/2 glugs of red wine (pinot noir, burgundy, or Chianti)
    olive oil

Make a mug of bouillon (you know, cube and boiling water in a mug?)

If you are using fresh oregano, finely mince half of it and set it aside.

Heat up a large stainless steel skillet over high heat (cast iron is not
your first choice this time, because you need quick response. God help you
if you're using an electric stove).

When it's hot, pour in enough olive oil to barely cover the bottom.

When the oil is hot:

If you had fresh oregano, take the half you didn't dice and put it in the
oil. Let it season the oil for a couple of minutes, then remove, shake the
oil back into the pan, and discard. Or, if you're crazy, set it aside, dice
it, and add when you add the rest of the oregano.

Throw in your Anaheim and jalapeno peppers.

Saute them for a moment, then add the onion. Swirl and stir the onion until
it starts to stick a little, then immediately turn the heat down to medium
or maybe a bit less, and add a couple tablespoon of chicken bouillon . (You
can also skip the bouillon and just use water. I tried wine once, but
didn't like it.)

Continue stirring until the bouillon is evaporated, then add another couple
of tablespoons, and stir some more.

Keep doing this until the onions are pulpy(that is, right before they turn
translucent. It isn't easy. If it makes you feel better, I can only hit it
about 50% of the time. It generally takes about 45 minutes.

While this is happening, get a large saucepan and pour in the cans of
tomatoey stuff. Add the minced garlic, the mushrooms, the oregano, the
basil (about 1/3 as much basil as you used oregano), the marjoram (even
less marjoram), cayenne to taste, crushed red pepper to taste, salt, black
pepper. For this, I tend to use ordinary table salt instead of kosher salt
or sea salt, I guess because the sausage is salty enough to bring the
flavors in the other stuff out. Freshly ground black pepper works best,
vide Alton Brown.

Add in the wine and water or the bouillon you didn't use; I tend to use
about half a can of liquid (wine + bouillon ). Heat medium low.

When the onions are perfect (or you've given up), add them to the sauce.

Turn the frying pan up to high, and fry up the sausage, then add it to the
sauce.

Add the peppers to the sauce. Add more water if necessary to cover.

Cook down until the consistency is right. Makes .8 fucktons (English
measure) on account of it's better the second day. Keep adding water when
you reheat it to keep the consistency right. You eat it over noodles, of
course.
