
\begin{recipe}{German Chocolate Cake}\tag{cake}
  \rating    4
  \nutrition 2
  \health    2
  \workload{medium}
  \time{60}
  \yield{9x13 inch cake}
  \servings{18--24 pieces}
  \source{Dean}
  \maketitle
  % \photo{}

  \begin{ingredients2}
    1 box & Betty Crocker mix, 15.25 \oz\\
    \twothird \cup & all-purpose flour\\
    2 \oz & baking chocolate\\
    \half \cup & butter\\
    1 \cup & coconut milk\\
    \threefourth \cup & milk\\
    4 & eggs
  \end{ingredients2}

  Combine dry goods in mixer bowl. In a large glass container, melt chocolate. Slowly
  stir in melted butter, milks, and beaten eggs. Pour liquids into mixer with dry
  ingredients and briefly mix.

  Pour into greased $9\times13$\inch baking pan and bake 30--35 minutes at
  \tempF[205]{350}.

  \begin{note}
    May replace 1~\cup coconut milk with an additional \threefourth~\cup milk.

    The variations from the box directions replace the water with things with more
    flavor and fat. Additionally we replace the oil with something with more flavor
    and that is solid at room temperatures. The added egg holds the extras together.
    Finally, additional flour is to get more cake and also to cut back on sweetness.
    We start with a box mix for all of the high-tech chemistry which makes a fluffy
    yet well-bonded cake (from-scratch cakes tend to be more crumbly)..
  \end{note}
\end{recipe}

% MODIFIED Alton Brown Devil's Food Cake (Chocolate Cake)
%   Was tasty but crumbly, I added an egg to combat that, so the following is untested.
%
% 300g br sugar
% 155g all purpose flour
% 113g cake flour
% 1t   baking soda
% 1/2c butter
% 1/2c oil
% 4oz  sour cream
% 3    eggs
% 2    egg yolks
% 4oz  chocolate
% 1c   coconut milk (or 3/4c milk)


\begin{recipe}{Coconut Pecan Frosting}\tag{frosting}
  \rating    5
  \nutrition 2
  \health    2
  \workload{medium}
  \time{20}
  \yield{frosting for 9x13 inch cake}
  \source{Dean}
  \maketitle
  % \photo{}

  \begin{ingredients2}
    6 \oz & evaporated milk\\
    3 \oz & coconut milk\\
    200 g & brown sugar\\
    \half \cup & butter\\
    3 & egg yolks\\
    1 \cup & pecans, chopped fine\\
    2 \cup & unsweetened coconut\\
    1 \T & vanilla
  \end{ingredients2}

  Stir together milks, sugar, butter, and eggs in large sauce pan. Stirring
  continuously, bring to temperature and cook at low boil for 15 minutes. Stir in
  rest of ingredients and cool.

  \begin{note}
    This produces a satisfying but slightly thin layer of frosting. If you want a
    thick layer of frosting, you might want to multiply the recipe by 1.5.
  \end{note}
\end{recipe}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../Cookbook"
%%% End:
