
\begin{recipe}{Marshmallows}
  \rating    4
  \nutrition 1
  \health    2
  \workload{medium}
  \time{39}
  \yield{1.5~\lb}
  \servings{12}
  \source{Alton Brown}
  \maketitle

  \begin{ingredients2}
    1 \cup & water (split)\\
    3 pkg & unflavored gelatin\\
    \fourth \cup & powdered sugar\\
    \fourth \cup & cornstarch\\
    1\half \cups & sugar\\
    1 \cup & light corn syrup\\
    pinch & salt\\
    1 \t & vanilla extract
  \end{ingredients2}

  Bloom gelatin in mixing bowl in \half~cup cold water. Combine powdered
  sugar and cornstarch. Sprinkle onto waxed paper in a 9x13 pan. Have wisk
  attachment ready!

  In a small saucepan combine \half~cup water, sugar, corn syrup, and salt.
  Cook covered over medium heat 3 to 4 minutes. Uncover, continue cooking
  to 240\degF using a candy thermometer. Immediately remove from heat.

  Mixer on low speed and slowly pour sugar mixture down side of mixing
  bowl into gelatin. Once fully added carefully increase speed to high.
  Whip until very thick and lukewarm (12 to 15 minutes).

  Add vanilla and continue mixing until incorporated. After whipping,
  spread mixture into pan and sprinkle powdered mixture on top. Save
  remaining powder for later.

  Set overnight. Cut into pieces using a pizza cutter, and coat with
  remaining powdered mixture.

  Miniature marshmallows: Pipe using \half~inch piping tip onto powdered
  waxed paper. After setting, cut and coat as above.
\end{recipe}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../Cookbook"
%%% End:
