
\begin{recipe}{Pho}%\tag{}
  \rating    4
  \nutrition 3
  \health    3
  \workload{heavy}
  \time{60}
  \yield{}
  \servings{4}
  \source{Hello Fresh / Internet}
  \maketitle
  % \photo{}

  \begin{ingredients2}
    2 & zucchini\\
    12 \oz & carrots\\
    3 \T & ponzu sauce\\
    2 & cinnamon sticks\\
    1 \T & coriander seeds\\
    6 & star anise\\
    % orig: 3 & whole cloves\\
    24 & cardamom seeds\\
    1 clove & garlic\\% orig: 2
    20 \oz & ground beef\\
    \half \cup & panko bread crumbs\\
    thumb & ginger\\
    4 \cups & veggie stock\\
    4 \cups & beef stock\\
    small & lime (opt)\\
    & chili flakes (opt)\\
    & bean sprouts (opt)\\
    & basil (opt)\\
    & green onions (opt)
  \end{ingredients2}

  \begin{itemize}[nosep]
  \item Stocks should be rich and flavorful. Meatballs can be replaced with
    beef brisket or sliced steak.

  \item Peel carrots and zucchini into ribbons. Marinade in half the ponzu.

  \item Mince ginger and chop onions.

  \item Form 12 meatballs from ground beef, panko, minced garlic, half the
    ginger, half the chives, the rest of the ponzu, and 6~\T veggie stock.

  \item Toast spices 3 minutes over medium-high heat. Remove from pot.

  \item Sear meatballs over medium-high heat in the soup pot.

  \item Remove meatballs. Fry onion whites until fragrant (30 sec). Add
    stocks and spices, bring to a boil. Simmer on low 30 min.

  \item Remove spice pods. Add meatballs (and any juice produced),
    remaining ginger, and continue cooking at low simmer for 10 min.

  \item Serve in bowls with zucchini and carrot ribbons. Lime slices and
    other ingredients are sprinkle-on decorations for personalization.
  \end{itemize}
\end{recipe}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../Cookbook"
%%% End:
