
\begin{recipe}{Shepherd's Pie}\tag{potato}\tag{lamb}
  \rating    5
  \nutrition 3
  \health    2
  \workload{medium}
  \time{90}
  \yield{$9\inch\times13\inch$ baking pan}
  \servings{6}
  \source{Alton Brown}
  % \photo{}
  \maketitle

  \begin{ingredients2}
    2 cloves & garlic, minced\\
    2 \lb & ground lamb\\
    \eigth \t & salt\\
    1\half \t & black pepper\\
    3 \T & flour\\
    2 \t & tomato paste or ketchup\\
    1 \cup & chicken broth\\
    2 \t & Worcestershire sauce\\
    2 \t & fresh chopped rosemary\\
    1 \t & fresh chopped thyme\\
    2 \cups & frozen mixed veggies\\
    2 \lb & russet potatoes\\
    \fourth \cup & half-and-half or milk\\
    2 \T & unsalted butter\\
    \fourth \t & black pepper
  \end{ingredients2}

  Preheat oven to 400\degF.

  Cook garlic, lamb, salt and pepper until browned and cooked through.
  Sprinkle on flour and toss to coat, continuing to cook for another
  minute. Add the tomato paste, chicken broth, Worcestershire, rosemary,
  thyme, and stir to combine. Bring to a boil, reduce the heat to low,
  cover and simmer slowly 10 to 12 minutes or until the sauce is thickened
  slightly. You may start the potatoes while simmering.

  Peel potatoes and cut into medium-sized chunks. Add to pot with just
  enough hot tap water to cover. Add several large pinches of salt to
  water. Bring to boil on high, but do not allow to come to full rolling
  boil (else will water-log). Potatoes should be ready after a few minutes
  at low boil. Drain potatoes and mash with half-and-half, butter and
  pepper. Add a bit of extra milk so that potatoes are a bit softer than
  one would normally make to ease spreading.

  Add veggies to the lamb mixture and spread evenly in glass baking dish.
  Top with the mashed potatoes. If mixture is close to the top of the pan,
  bake over a drip pan or foil. Bake 25 minutes or just until the potatoes
  begin to brown. Remove to a cooling rack for at least 15 minutes before
  serving.
\end{recipe}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../Cookbook"
%%% End:
