
\begin{recipe}{Steak au poivre}%\tag{}
  \rating    3
%   \nutrition
%   \health
  \workload{light}
  \time{60}
%   \yield{}
%   \servings{}
  \source{Alton Brown}
  \maketitle
  % \photo{}

  \begin{ingredients2}
    4 & 6--8 \oz steaks\\
    2 \T & whole peppercorns\\
    1 \T & unsalted butter\\
    1 \t & olive oil\\
    \third \cup & Cognac or brandy\\
    1 \cup & heavy cream
  \end{ingredients2}

  Steaks should be no more than 1\half inches thick. Remove steaks from
  refrigerator 30--60 minutes prior to cooking. Sprinkle all sides with
  salt.

  Coarsely crush the peppercorns (in a bag with with mallet or bottom of
  cast iron skillet). Spread evenly onto a plate and press fillets, on both
  sides, into the pepper until it coats the surface. Set aside.

  In medium skillet over medium heat, melt the butter and olive oil. As
  soon as the butter and oil begin to turn golden and smoke, gently place
  the steaks in the pan. For medium-rare, cook for 4 minutes on each side.
  Once done, remove the steaks to a plate, tent with foil and set aside.
  Pour off any excess fat but do not wipe or scrape the pan clean.

  \textsl{Off of the heat}, add Cognac to the pan and \textsl{immediately}
  ignite the alcohol with a long match or firestick. Gently shake pan until
  the flames die. Return the pan to medium heat and add the cream. Bring
  the mixture to a boil and whisk until the sauce coats the back of a
  spoon, approximately 5--6 minutes. Add a teaspoon of Cognac and season,
  to taste, with salt. Add the steaks back to the pan, spoon the sauce
  over, and serve.
\end{recipe}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../Cookbook"
%%% End:
